Rotating Stars from \Kepler Observed with Gaia DR1

### 2016-10-14 paper/ms.tex
adding more text

@@

\begin{figure}[]
\centering
\includegraphics[width=5.3in]{fig2.png}
\caption{
isochrones from \citet{bressan2012}
}
\label{fig:HR}
\end{figure}

\begin{figure}[]
\centering
\includegraphics[width=4in]{fig3.png}
\caption{
}
\label{fig:hist}
\end{figure}

@@

\begin{figure}[]
\centering
\includegraphics[width=5.3in]{fig4.png}
\caption{ Rotation period versus temperature for TGAS-matched stars near the isochrone main sequence (blue circles). Distributions of rotation periods for these main sequence selected stars are shown as vertical histograms for 7 bins of temperature (black lines), with each temperature bin having equal numbers of stars. As in Figure \ref{fig:all}, the full \Kepler--Gaia matched sample is shown for reference (small black dots). The bimodality in rotation periods previously seen by \citet{mcquillan2014} extends the full range of temperatures in the \Kepler--Gaia main sequence sample shown here.
A \citet{meibom2011} 600 Myr gyrochonology-isochrone roughly traces the bimodality midpoint up to 6000 K (red solid line). A log-linear extrapolation to 6500 K (red dashed line) continues to track the bimodality to hotter temperatures, and roughly traces a line of constant Rossby number.
}
\label{fig:gyro}
\end{figure}

>>>>

% (gaia[u'parallax_error'] < 0.4) &
  %            (gaia[u'phot_g_mean_flux_error']/gaia[u'phot_g_mean_flux'] < 0.01))

@@

%%%%%
\begin{figure}[]
\centering
\includegraphics[width=5.3in]{fig2.png}
\caption{Hertzsprung--Russell (HR) diagram using temperatures from \citet{mcquillan2014} and Gaia DR1 $G$-band absolute magnitudes for the 894 stars that pass photometric and parallax quality cuts described in the text. Points are colored by their measured \Kepler rotation periods. Two isochrones from \citet{bressan2012} are shown, with ages of 300 Myr and 4 Gyr (solid and dashed lines).
}
\label{fig:HR}
\end{figure}

%%%%%
\begin{figure}[]
\centering
\includegraphics[width=4in]{fig3.png}
\caption{Distribution of differences between the Gaia DR1 $G$ absolute magnitudes and values for main sequence stars from the 300 Myr isochrone shown in Figure \ref{fig:HR}. The range of sources selected near the single star main sequence (red lines) may have additional contamination due to dust extinction and binary companions.}
\label{fig:hist}
\end{figure}

@@

%%%%%
\begin{figure}[]
\centering
\includegraphics[width=5.3in]{fig4.png}
\caption{ Rotation period versus temperature for TGAS-matched stars near the isochrone main sequence (blue circles). Distributions of rotation periods for these main sequence selected stars are shown as vertical histograms for 7 bins of temperature (black lines), with each temperature bin having equal numbers of stars. As in Figure \ref{fig:all}, the full \Kepler--Gaia matched sample is shown for reference (small black dots). The bimodality in rotation periods previously seen by \citet{mcquillan2014} extends the full range of temperatures in the \Kepler--Gaia main sequence sample shown here.
A \citet{meibom2011} 600 Myr gyrochonology-isochrone roughly traces the bimodality midpoint up to 6000 K (red solid line). A log-linear extrapolation to 6500 K (red dashed line) continues to track the bimodality to hotter temperatures, and roughly traces a line of constant Rossby number.
}
\label{fig:gyro}
\end{figure}
